\documentstyle[12pt]{article}
\pagestyle{empty}
\textwidth=450pt
\textheight=650pt
\topmargin=-40pt
\oddsidemargin=10pt
\begin{document}
%\baselineskip=20pt
\parskip=7pt
\parindent=0pt
\begin{center}
{\bf University of Colorado} \\
{\bf Department of Computer Science}\\
\medskip 
{\bf Chaotic Dynamics -- CSCI 4446/6446} \\
{\bf Spring 2003} \\
\medskip 
Midterm Evaluation
\end{center}
\medskip

\begin{enumerate}

\item Are you happy with the amount that you're learning?
\bigskip
\item Are you happy with the amount of feedback you're getting
about your performance?
\bigskip
\item Is the grading policy clear and sensible?
\bigskip

\item Is the problem set grading fair and useful?
\bigskip

\item Would handed-out problem set solutions help you a lot?
\bigskip

\item How long did problem set 7 (variational equation) take you?
Please decompose this number into reading/thinking/programming/CPU
time.
\bigskip

\item How long did problem set 6 (Poincar\'{e} sections) take you?
(Same decomposition.)
\bigskip

\item If you have punted one or more problem sets, please 
explain why.
\bigskip
\bigskip
\bigskip

\item Please list any parts of any problem sets 
\begin{enumerate}
\item that were frustrating
\bigskip
\bigskip
\bigskip
\item that you don't feel you learned much from
\end{enumerate}
\bigskip
\bigskip
\bigskip

\item Please comment on the usefulness, readability, interest quotient, 
etc., of the following readings:
\begin{enumerate}
\item Strogatz
\bigskip
\item books on reserve
\bigskip
\item course pack
\bigskip
\item notes on webpage
\bigskip
\item supplemental links on webpage
\bigskip
\end{enumerate}

\item Can you think of any warnings/suggestions/clarifications that 
should be put in the first-day syllabus? (e.g., ``expect to spend
n hours per week debugging code...''  ``the workload is heavy for
the first 2/3 of the semester and light afterwards'')
\bigskip
\bigskip
\bigskip
\bigskip

\item Were any of the lecture topics uninteresting or non-useful?  Were
there other topics that you'd like to see covered?
\bigskip
\bigskip

\item Does the mix of grads and undergrads impede your learning?
If so, can you suggest a solution?
\bigskip
\bigskip

\end{enumerate}

Please use the rest of this sheet (plus additional sheets, if
necessary) to elaborate upon your responses to these questions and
propose fixes or solutions to problems.  The LaTeX source for this
document will be available on the course webpage for anyone who
doesn't want to hand-write their answers.

\end{document}
